---
title: "Sampling clients for phone surveys in resource-poor settings: insights from PMA client data"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      results="hide",
                      comment = "",
                      message = FALSE,
                      warning = FALSE)

knitr::opts_knit$set(root.dir = "~/Dropbox/0iSquared/iSquared_PMA/PMA_QoC_Followup/")

Sys.setenv(TZ='EST')
time<-Sys.time()
date<-as.Date(Sys.time(	), format='%d%b%Y')

suppressWarnings(suppressMessages(library(dplyr)))
suppressWarnings(suppressMessages(library(tidyverse)))
suppressWarnings(suppressMessages(library(data.table)))
suppressWarnings(suppressMessages(library(readxl)))
suppressWarnings(suppressMessages(library(janitor)))

suppressWarnings(suppressMessages(library(ggplot2)))
suppressWarnings(suppressMessages(library(plotly)))
suppressWarnings(suppressMessages(library(knitr)))  
suppressWarnings(suppressMessages(library(kableExtra)))  

suppressWarnings(suppressMessages(library(RColorBrewer))) 

suppressWarnings(suppressMessages(library(networkD3))) #for Sankey
```
(Last updated on `r date`)   

```{r setupcolor}
#['#f7fbff','#deebf7','#c6dbef','#9ecae1','#6baed6','#4292c6','#2171b5','#08519c','#08306b']

bluecolors <- brewer.pal(7,"Blues")
greencolors <- brewer.pal(7,"Greens")
orangecolors <- brewer.pal(7,"Oranges")
redcolors <- brewer.pal(7,"Reds")
divcolors<-brewer.pal(7,"RdYlBu")

```

```{r directory}
#dir("~/Dropbox/0 iSquared/iSquared_PMA/PMA_QoC_Followup/")
pathfile<-"./Understanding_CEI_Sample.xlsx"
excel_sheets(pathfile)
```

### 1. Why this anaysis? 
<div class="alert alert-info">
**What is this analysis for?** 

There's rapidly growing interest to measure and understand quality of care - especially experience among clients. However, it is challenging to conduct conventional client exit interviews in many low-resource settings due to resource constraints, and innovative approaches have been used to obtain information from clients such as SMS, phone interviews, and surveys on social media platforms. 

However, client sampling faces many challenges from getting a good quality sampling frame to low contact and response rates. Critical remaining questions are **how much bias is in samples of such assessments**, and **if (and how much) the sample bias matters to understand clients' experience of care**. 

We explore these questions, using PMA family planning client data from four countries/geographies: Burkina Faso, Kenya, and two states in Nigeria, Kano and Lagos.   
</div>

Note:    
1. Implications from this analysis would be most appropriate for phone surveys, since other modes have additional barriers such as literacy and use of social media.   
2. For more information on the PMA, [see here](www.pmadata.org).    
3. For PMA client sampling methods, [see here](https://rpubs.com/YJ_Choi/PMA_CEI_Sample).      

### 2. Data and methods

PMA client data are collected at two time points using different modes:   
1. **Face-to-face interview - at the end of facility visit**. Response rates are typically very high in all settings.      
2. **Follow-up phone interview - 4 to 6 months after the visit**. On average across countries/geographies, roughly 70% of clients completed the phone follow-up.  

For illustrative purposes, we can treat the **exit interview data <span style="color: #238B45;">(green left panel below)</span>** as sampling framework for a potential client phone survey, and the **phone follow-up interview <span style="color: #084594;">(navy blue part on the right panel)</span>** as a sample of clients who completed the phone survey. 

```{r SankeyExample, results='asis'}
dta<-read_excel(path = pathfile,
                sheet = "Table3",
                col_names = TRUE, 
                range = "A1:K12")%>%
    filter(xsurvey=="ALL")%>%
    select(xsurvey, starts_with("pct_"))%>%
    mutate(
        xsurvey="Clients.interviewed.at.exit"
    )%>%
    rename(
        No.consent.for.phone.interview = pct_noconsent, 
        No.access.to.phone = pct_nophone,
        No.FP.method = pct_nomethod,
        Lost.to.follow.up = pct_lost,
        Completed.phone.interview = pct_ceifu
    )

matrix<-dta %>% 
    remove_rownames %>% 
    column_to_rownames(var="xsurvey")

# Libraries
library(tidyverse)
library(networkD3)

# Reshape the matrix data to long format 
data_long <- matrix %>%
    rownames_to_column %>%
    gather(key = 'key', value = 'value', -rowname) %>%
    filter(value > 0)
colnames(data_long) <- c("source", "target", "value")
data_long$target <- paste(data_long$target, " ", sep="")

# Create a node data frame, listing every entities involved in the flow
nodes <- data.frame(name=c(as.character(data_long$source),
                           as.character(data_long$target)) %>%
                        unique()
                    )

# With networkD3, connection must be provided using id, not using real name like in the links dataframe. So we need to reformat it.
data_long$IDsource=match(data_long$source, nodes$name)-1 
data_long$IDtarget=match(data_long$target, nodes$name)-1

# Prepare colour scale (7-class Greens and Blues)
ColourScal ='d3.scaleOrdinal() .range([
        "#238B45", 
        "#C6DBEF", "#9ECAE1", "#6BAED6", "#4292C6", "#084594"])'

# Make the Network
# set "iterations=0" to avoid automatic assignment of the box order
sankeyNetwork(Links = data_long, Nodes = nodes,
            Source = "IDsource", Target = "IDtarget",
            Value = "value", NodeID = "name", 
            sinksRight=FALSE, colourScale=ColourScal, 
            nodeWidth=40, fontSize=13, nodePadding=20,
            iterations=0
            )
```

<div class="alert alert-info">

**Questions and Methods**  

1. How much background characteristics change between the sampling frame and final sample of a client phone survey? Considering that access to a phone is required but not necessarily universal in certain settings, it may results in a sample that is more likely to be wealthy and educated than those who are not included in the sample.    

_Analysis_: We compare demographic and socioeconomic characteristics of those included vs. excluded in the sample.    

2. Does the sample produce biased measures? *Ideally,* there should be equal (and high) quality of care - both experience and process of care - regardless of clients' characteristics. If that holds true, biased sample may not be detrimental to assess and monitor.       

_Analysis_: We compare both satisfaction (measured using a four-point Likert scale) and experience (using 10-item quality of contraceptive counseling) between those included vs. excluded in the sample.  

*All data on demographic and socioeconomic characteristics and quality of care come from exit interview data in four countries/geographies: Burkina Faso, Kenya, and two states in Nigeria, Kano and Lagos.*  
</div>

### 3.0. What would be the response rate?   

```{r dta_Table2, restuls='hide', fig.width=5, fig.height=3}
dta<-read_excel(path = pathfile,
                sheet = "Table2",
                col_names = TRUE, 
                range = "A1:K12")%>%
    mutate(
        survey="", 
        survey=ifelse(xsurvey=="BFP2", "Burkina Faso",
                      ifelse(xsurvey=="KEP2", "Kenya",
                             ifelse(xsurvey=="NGKanoP2", "Nigeria, Kano",        
                                    ifelse(xsurvey=="NGLagosP2", "Nigeria, Lagos",      
                                           survey))))
    )

dta%>%
    plot_ly(
        y = ~survey,
        type="bar",
        x = ~pct_ceifu, name = "Completed phone interview",
        marker = list(color = bluecolors[7]), 
        text = ~pct_ceifu, 
        textposition = 'outside', 
        textfont = list(size= c(12))
    )%>%
    layout(
        xaxis=list(title = "<b>% of clients**</b>", range = c(0, 100)), 
        yaxis=list(title = "", autorange = "reversed") 
    )
```

```{r dta_Table3, results='asis', fig.width=8, fig.height=3}
dta<-read_excel(path = pathfile,
                sheet = "Table3",
                col_names = TRUE, 
                range = "A1:K12")%>%
    mutate(
        survey="", 
        survey=ifelse(xsurvey=="ALL", "All",
                      ifelse(xsurvey=="BFP2", "Burkina Faso",
                             ifelse(xsurvey=="KEP2", "Kenya",
                                    ifelse(xsurvey=="NGKanoP2", "Nigeria, Kano",        
                                           ifelse(xsurvey=="NGLagosP2", "Nigeria, Lagos",      
                                                  survey)))))
    )

#dta$survey<-factor(dta$survey, 
#                   levels = unique(dta$survey) 
#                   [order(dta$pct_ceifu, decreasing = FALSE)])

dta%>%
    filter(survey!="All")%>%
    plot_ly(
        x = ~survey,
        type="bar", 
        y = ~pct_ceifu, name = "Completed phone survey",
        marker = list(color = bluecolors[7]), 
        #text = ~round(pct_ceifu, 0), 
        #textposition = 'outside', 
        #textfont = list(size= c(12))
        )%>%         
    add_trace(y = ~pct_lost, 
              name = "Lost to follow up",
              marker = list(color = bluecolors[5]))%>%       
    add_trace(y = ~pct_nophone, 
              name = "No FP method*",
              marker = list(color = bluecolors[3]))%>%         
    add_trace(y = ~pct_nophone, 
              name = "No access to phone",
              marker = list(color = bluecolors[3]))%>%       
    add_trace(y = ~pct_noconsent, 
              name = "No consent",
              marker = list(color = bluecolors[2]))%>%       
    layout(
        barmode = 'stack', 
        paper_bgcolor='#FAFAFA', plot_bgcolor='#FAFAFA',
        legend = list(x = 100, y = 0.5), 
        yaxis=list(title = "<b>% of clients</b>", range = c(0, 100)), 
        xaxis=list(title = "") 
    )
```
Note: PMA phone follow up was done only women who received contraceptive method(s) or prescription at the facility visit.  

### 3.1. How different are those who are included vs. excluded in the sample? 
<div class="alert alert-danger">
Clients in the sample tend to: perceive themselves to be wealthier, have higher education, and be older. But, the differences are not statistically significant in most cases. </div>
```{r dta_Table4}
dta<-read_excel(path = pathfile,
                sheet = "Table4",
                col_names = TRUE, 
                range = "A1:K12")%>%
    filter(xsurvey!="")%>%
    mutate(
        ceipfu= "", 
        ceipfu=ifelse(ceifu==1, "Phone interview",
                      ifelse(ceifu==0, "No phone interview",         
                             ceipfu)), 
        survey="", 
        survey=
            ifelse(xsurvey=="BFP2", "Burkina Faso",
                   ifelse(xsurvey=="KEP2", "Kenya",
                          ifelse(xsurvey=="NGKanoP2", "Nigeria, Kano",        
                                 ifelse(xsurvey=="NGLagosP2", "Nigeria, Lagos",      
                                        survey))))
    )


library("reshape2")
dtatemp<-dta%>%select(survey, ceifu, starts_with(c("pct_", "mean_")))

dtawide<-dcast(melt(dtatemp, 
                    id.vars=c("survey", "ceifu")), 
               survey~variable+ceifu)
```

```{r dta_Table4_hhladder, results='hide', fig.width=8, fig.height=4}
panel <- . %>% 
    plot_ly(
        y = ~ceipfu,
        type="bar",
        x = ~pct_hhladder_6higher, 
        marker = list(color = bluecolors[4]),  
        text = ~round(pct_hhladder_6higher, 0), 
        textposition = 'outside', 
        textfont = list(size= c(12))
    )%>%
    add_annotations(
        text = ~unique(survey),
        y = 0.5, x = 0.95, xref = "paper", yref = "paper",   
        xanchor = "center", yanchor = "bottom", showarrow = FALSE,
        font = list(size = 12)
    ) %>%    
    layout(
        xaxis=list(title = "<b>% of clients who perceive their household wealth is above median</b>", range = c(0, 100)), 
        yaxis=list(title = "") 
    )

dta%>%
    group_by(survey) %>%
    do(p = panel(.)) %>%
    subplot(nrows = 4, shareX = TRUE, shareY = TRUE) %>% 
    layout(
        showlegend=FALSE,  
        title = "")
```

```{r dta_Table4_edu, results='hide', fig.width=8, fig.height=4}
panel <- . %>% 
    plot_ly(
        y = ~ceipfu,
        type="bar",
        x = ~pct_edu_sec_more, 
        marker = list(color = bluecolors[4]),  
        text = ~round(pct_edu_sec_more, 0), 
        textposition = 'outside', 
        textfont = list(size= c(12))
    )%>%
    add_annotations(
        text = ~unique(survey),
        y = 0.5, x = 0.95, xref = "paper", yref = "paper",   
        xanchor = "center", yanchor = "bottom", showarrow = FALSE,
        font = list(size = 12)
    ) %>%    
    layout(
        xaxis=list(title = "<b>% of clients who attended secondary school or higher</b>", range = c(0, 100)), 
        yaxis=list(title = "") 
    )

dta%>%
    group_by(survey) %>%
    do(p = panel(.)) %>%
    subplot(nrows = 4, shareX = TRUE, shareY = TRUE) %>% 
    layout(
        showlegend=FALSE,  
        title = "")
```

```{r dta_Table4_phone, results='hide', fig.width=8, fig.height=4}
dta%>% 
    filter(ceifu==0)%>%
    plot_ly(
        y = ~survey,
        type="bar",
        x = ~pct_ownphone, 
        marker = list(color = bluecolors[4]),  
        text = ~round(pct_ownphone, 0), 
        textposition = 'outside', 
        textfont = list(size= c(12))
    ) %>%    
    layout(
        xaxis=list(title = "<b>% of clients who did not have phone interview</b>", range = c(0, 100)), 
        yaxis=list(title = "") 
    )
```

```{r dta_Table4_age, results='hide', fig.width=8, fig.height=4}
panel <- . %>% 
    plot_ly(
        y = ~ceipfu,
        type="bar",
        x = ~mean_age_in_years, 
        marker = list(color = bluecolors[4]),  
        text = ~round(mean_age_in_years, 0), 
        textposition = 'outside', 
        textfont = list(size= c(12))
    )%>%
    add_annotations(
        text = ~unique(survey),
        y = 0.5, x = 0.95, xref = "paper", yref = "paper",   
        xanchor = "center", yanchor = "bottom", showarrow = FALSE,
        font = list(size = 12)
    ) %>%    
    layout(
        xaxis=list(title = "<b>Mean age (years)</b>", range = c(0, 40)), 
        yaxis=list(title = "") 
    )

dta%>%
    group_by(survey) %>%
    do(p = panel(.)) %>%
    subplot(nrows = 4, shareX = TRUE, shareY = TRUE) %>% 
    layout(
        showlegend=FALSE,  
        title = "")
```

```{r dta_Table4_wide_hhladder6, results='hide', fig.width=8, fig.height=4}
dtawide%>%
    plot_ly(
        y = ~survey,
        type="bar",
        x = ~pct_hhladder_6higher_0, name = "No phone interview",
        marker = list(color = bluecolors[4]),  
        text = ~round(pct_hhladder_6higher_0, 0), 
        textposition = 'outside', 
        textfont = list(size= c(12)) )%>%
    add_bars( x = ~pct_hhladder_6higher_1, name = "Phone interview",
              marker = list(color = bluecolors[7]),
              text = ~round(pct_hhladder_6higher_1, 0),
              textposition = 'outside', 
              textfont = list(size= c(12)))%>%      
    layout(
        legend = list(x = 100, y = 0.5), 
        xaxis=list(title = "<b>% of clients who perceive their household wealth is above median</b>", 
                   range = c(0, 100)), 
        yaxis=list(title = "", autorange = "reversed") 
    )
```

```{r dta_Table4_wide_hhladder5, results='asis', fig.width=8, fig.height=4}
dtawide%>%
    plot_ly(
        y = ~survey,
        type="bar",
        x = ~pct_hhladder_5higher_0, name = "No phone interview",
        marker = list(color = bluecolors[4]),  
        text = ~round(pct_hhladder_5higher_0, 0), 
        textposition = 'outside', 
        textfont = list(size= c(12)) )%>%
    add_bars( x = ~pct_hhladder_5higher_1, name = "Phone interview",
              marker = list(color = bluecolors[7]),
              text = ~round(pct_hhladder_5higher_1, 0),
              textposition = 'outside', 
              textfont = list(size= c(12)))%>%      
    layout(
        paper_bgcolor='#FAFAFA', plot_bgcolor='#FAFAFA',
        legend = list(x = 100, y = 0.5), 
        xaxis=list(title = "<b>% of clients who perceive their household wealth is median or higher</b>", 
                   range = c(0, 100)), 
        yaxis=list(title = "", autorange = "reversed") 
    )
```
Note: The difference in perceived wealth median or above is statistically significant in **Kenya** and **Lagos, Nigeria** (Chi-square P-value < 0.05). 

```{r dta_Table4_wide_hhladder, results='hide', fig.width=8, fig.height=4}
dtawide%>%
    plot_ly(
        y = ~survey,
        type="bar",
        x = ~mean_hhladder_0, name = "No phone interview",
        marker = list(color = bluecolors[4]),  
        text = ~round(mean_hhladder_0, 1), 
        textposition = 'outside', 
        textfont = list(size= c(12)) )%>%
    add_bars( x = ~mean_hhladder_1, name = "Phone interview",
              marker = list(color = bluecolors[7]),
              text = ~round(mean_hhladder_1, 1),
              textposition = 'outside', 
              textfont = list(size= c(12)))%>%      
    layout(
        paper_bgcolor='#FAFAFA', plot_bgcolor='#FAFAFA',
        legend = list(x = 100, y = 0.5), 
        xaxis=list(title = "<b>Mean perceived household welath (range: 1-10)</b>", 
                   range = c(1, 10)), 
        yaxis=list(title = "", autorange = "reversed") 
    )

#Note: The difference in perceived wealth ranking is statistically significant in **Kenya** and **Kano, Nigeria** (Chi-square P-value < 0.05). 
```

```{r dta_Table4_wide_edu, results='asis', fig.width=8, fig.height=4}
dtawide%>%
    plot_ly(
        y = ~survey,
        type="bar",
        x = ~pct_edu_sec_more_0 , name = "No phone interview",
        marker = list(color = bluecolors[4]),  
        text = ~round(pct_edu_sec_more_0 , 0), 
        textposition = 'outside', 
        textfont = list(size= c(12)) )%>%
    add_bars( x = ~pct_edu_sec_more_1 , name = "Phone interview",
              marker = list(color = bluecolors[7]),
              text = ~round(pct_edu_sec_more_1 , 0),
              textposition = 'outside', 
              textfont = list(size= c(12)))%>%      
    layout(
        paper_bgcolor='#FAFAFA', plot_bgcolor='#FAFAFA',  
        legend = list(x = 100, y = 0.5), 
        xaxis=list(title = "<b>% of clients who attended secondary school or higher</b>",
                   range = c(0, 100)), 
        yaxis=list(title = "", autorange = "reversed") 
    )
```
Note: The difference in attending secondary school or higher is statistically significant **all countries/geographies** (Chi-square P-value < 0.05). 

```{r dta_Table4_wide_age, results='asis', fig.width=8, fig.height=4}
dtawide%>%
    plot_ly(
        y = ~survey,
        type="bar",
        x = ~mean_age_in_years_0, name = "No phone interview",
        marker = list(color = bluecolors[4]),  
        text = ~round(mean_age_in_years_0, 1), 
        textposition = 'outside', 
        textfont = list(size= c(12)) )%>%
    add_bars( x = ~mean_age_in_years_1, name = "Phone interview",
              marker = list(color = bluecolors[7]),
              text = ~round(mean_age_in_years_1, 1),
              textposition = 'outside', 
              textfont = list(size= c(12)))%>%      
    layout(
        paper_bgcolor='#FAFAFA', plot_bgcolor='#FAFAFA',  
        legend = list(x = 100, y = 0.5), 
        xaxis=list(title = "<b>Mean age (years)</b>", range = c(0, 40)), 
        yaxis=list(title = "", autorange = "reversed") 
    )
```
Note: The difference in age is statistically significant in **Kenya** and **Lagos, Nigeria** (T-test with unequal variance P-value < 0.05). 

### 3.2. Is quality of care different between those who are included vs. excluded in the sample?   
<div class="alert alert-danger">
- Clients in the sample are more likely to report to be 'very satisfied' but the differences are not statistically significant.   
- Clients in the sample have reported slightly higher experience of care but the differences are neither meaningful nor statistically significant.   
</div>
```{r dta_Table5}
dta<-read_excel(path = pathfile,
                sheet = "Table5",
                col_names = TRUE, 
                range = "A1:K12")%>%
    filter(xsurvey!="")%>%
    mutate(
        ceipfu= "", 
        ceipfu=ifelse(ceifu==1, "Phone interview",
                      ifelse(ceifu==0, "No phone interview",         
                             ceipfu)), 
        survey="", 
        survey=
            ifelse(xsurvey=="BFP2", "Burkina Faso",
                   ifelse(xsurvey=="KEP2", "Kenya",
                          ifelse(xsurvey=="NGKanoP2", "Nigeria, Kano",        
                                 ifelse(xsurvey=="NGLagosP2", "Nigeria, Lagos",      
                                        survey))))
    )

dtatemp<-dta%>%select(survey, ceifu, starts_with(c("pct_", "qcc__")))

dtawide<-dcast(melt(dtatemp, 
                    id.vars=c("survey", "ceifu")), 
               survey~variable+ceifu)
```

```{r dta_Table5_verysatisfied, results='hide', fig.width=8, fig.height=4}
panel <- . %>% 
    plot_ly(
        y = ~ceipfu,
        type="bar",
        x = ~pct_verysatisfied, 
        marker = list(color = redcolors[4]),  
        text = ~round(pct_verysatisfied, 0), 
        textposition = 'outside', 
        textfont = list(size= c(12))
    )%>%
    add_annotations(
        text = ~unique(survey),
        y = 0.5, x = 0.95, xref = "paper", yref = "paper",   
        xanchor = "center", yanchor = "bottom", showarrow = FALSE,
        font = list(size = 12)
    ) %>%    
    layout(
        xaxis=list(title = "<b>% of clients who reported to be very satisfied</b>", 
                   range = c(0, 100)), 
        yaxis=list(title = "") 
    )

dta%>%
    group_by(survey) %>%
    do(p = panel(.)) %>%
    subplot(nrows = 4, shareX = TRUE, shareY = TRUE) %>% 
    layout(
        showlegend=FALSE,  
        title = "")
```

```{r dta_Table5_qcc, results='hide', fig.width=8, fig.height=4}
panel <- . %>% 
    plot_ly(
        y = ~ceipfu,
        type="bar",
        x = ~qcc__mean, 
        marker = list(color = redcolors[4]),  
        text = ~round(qcc__mean, 2), 
        textposition = 'outside', 
        textfont = list(size= c(12))
    )%>%
    add_annotations(
        text = ~unique(survey),
        y = 0.5, x = 0.95, xref = "paper", yref = "paper",   
        xanchor = "center", yanchor = "bottom", showarrow = FALSE,
        font = list(size = 12)
    ) %>%    
    layout(
        xaxis=list(title = "<b>Mean QCC score (range: 1-4)</b>", range = c(1, 4)), 
        yaxis=list(title = "") 
    )

dta%>%
    group_by(survey) %>%
    do(p = panel(.)) %>%
    subplot(nrows = 4, shareX = TRUE, shareY = TRUE) %>% 
    layout(
        showlegend=FALSE,  
        title = "")
```

```{r dta_Table5_wide_verysatisfied, results='asis', fig.width=8, fig.height=4}
dtawide%>%
    plot_ly(
        y = ~survey,
        type="bar",
        x = ~pct_verysatisfied_0, name = "No phone interview",
        marker = list(color = bluecolors[4]),  
        text = ~round(pct_verysatisfied_0, 0), 
        textposition = 'outside', 
        textfont = list(size= c(12)) )%>%
    add_bars( x = ~pct_verysatisfied_1, name = "Phone interview",
              marker = list(color = bluecolors[7]),
              text = ~round(pct_verysatisfied_1, 0),
              textposition = 'outside', 
              textfont = list(size= c(12)))%>%      
    layout(
        paper_bgcolor='#FAFAFA', plot_bgcolor='#FAFAFA',
        legend = list(x = 100, y = 0.5), 
        xaxis=list(title = "<b>% of clients who reported to be very satisfied</b>", 
                   range = c(0, 100)), 
        yaxis=list(title = "", autorange = "reversed") 
    )
```
Note: The difference in reporting to be very satisfied is statistically significant in **Burkina Faso** and **Kenya** (T-test P-value < 0.05). 

```{r dta_Table5_wide_qcc, results='asis', fig.width=8, fig.height=4}
dtawide%>%
    plot_ly(
        y = ~survey,
        type="bar",
        x = ~qcc__mean_0, name = "No phone interview",
        marker = list(color = bluecolors[4]),  
        text = ~round(qcc__mean_0, 2), 
        textposition = 'outside', 
        textfont = list(size= c(12)) )%>%
    add_bars( x = ~qcc__mean_1, name = "Phone interview",
              marker = list(color = bluecolors[7]),
              text = ~round(qcc__mean_1, 2),
              textposition = 'outside', 
              textfont = list(size= c(12)))%>%      
    layout(
        paper_bgcolor='#FAFAFA', plot_bgcolor='#FAFAFA',
        legend = list(x = 100, y = 0.5), 
        xaxis=list(title = "<b>Mean QCC score (range: 1-4)</b>",
                   range = c(1, 4)), 
        yaxis=list(title = "", autorange = "reversed") 
    )
```
Note: The difference in the QCC score is statistically significant in **Kenya** (T-test with unequal variance P-value < 0.05). 

### 4. Implications to design a client surveys via remote data collection 

- Access to phone is still a barrier among female clients in certain low resource settings such as Kano, Nigeria (remote rural state) and Burkina Faso (with relatively less resources).    
- The phone survey samples are biased in terms of wealth, education, and age.   
- However, there is no statistically significant or programmatically meaningful differences in terms of self-reported satisfaction and experience of care.   

### 5. Limitations and methodological note  
1. How strong is the assumption? This exercise is reasonably acceptable, if:  
(1) sample recruitment is done actively in-person - *as opposed to more passive approaches such as relying on clients scanning QR code*; and   
(2) the data collection is done via computer assisted telephone interviewing (CATI) - *as opposed to using short message services (SMS), self-administered web-based interview, or interactive voice response interviews*.   

2. In PMA client sample follow-up, length of follow-up interval ranged from 4 to 6 months. With incentives and shorter interval between sampling and interview, contact rate - and subsequently response rate - may be higher.    
```{r showinterval, results="asis"}
dta<-read_excel(path = pathfile,
                sheet = "Table2",
                col_names = TRUE, 
                range = "A1:K12")%>%
    mutate(
        survey="", 
        survey=ifelse(xsurvey=="BFP2", "Burkina Faso",
               ifelse(xsurvey=="KEP2", "Kenya",
               ifelse(xsurvey=="NGKanoP2", "Nigeria, Kano",        
               ifelse(xsurvey=="NGLagosP2", "Nigeria, Lagos",      
                      survey))))
    )%>%
    filter(survey!="")%>%
    select(survey, interval_in_months)

kable(dta, 
      caption = "Mean length of follow-up interval in months by survey")%>%
    column_spec(1, width = "20em")%>%
    column_spec(1, width = "20em")%>%
    kable_styling(bootstrap_options = c("hover", "condensed"), 
                  position = "left",
                  full_width = F)

```

3. PMA client sample is convenient random sample, conducted in a subset of facilities sampled for facility assessment (see below bar graph). The client sampling frame is FP clients who attended medium-to-high volume facilities. Thus, it systematically excludes those who visit small and/or lower level facilities. In addition, no client data were collected from pharmacies.   

However, it is suggested that back ground characteristics of this sample are by and large similar to those who obtained contraception in the relatively recent time period at the population level. [see here](https://rpubs.com/YJ_Choi/PMA_CEI_Sample)  
```{r dta_Table1, results='asis', fig.width=5, fig.height=3}
dta<-read_excel(path = pathfile,
                sheet = "Table1",
                col_names = TRUE, 
                range = "A1:K12")%>%
    mutate(
        survey="", 
        survey=ifelse(xsurvey=="BFP2", "Burkina Faso",
                      ifelse(xsurvey=="KEP2", "Kenya",
                             ifelse(xsurvey=="NGKanoP2", "Nigeria, Kano",        
                                    ifelse(xsurvey=="NGLagosP2", "Nigeria, Lagos",      
                                           survey))))
    )

dta%>%
    filter(SDPtype=="All")%>%
    plot_ly(
        y = ~survey,
        type="bar",
        x = ~pct_cei, name = "CEI conducted in the facility",
        marker = list(color = bluecolors[5]), 
        text = ~pct_cei, 
        textposition = 'outside', 
        textfont = list(size= c(12))
    )%>%
    layout(
        legend = list(x = 100, y = 0.5), 
        xaxis=list(title = "<b>% of health facilities where clients exit interviews were conducted</b>", 
                   range = c(0, 100)), 
        yaxis=list(title = "", autorange = "reversed") 
    )
```

